---
title: "Analisis Image dengan menggunakan EBimage"
author: "Mila Amarila P"
date: "14 Maret 2021"
output: html_document
---


proses Import image 
```{r}
library(EBImage)
Image <- readImage("D:/Rmarkdown/analisisEBimage/foto2.jpg")
print(Image)
display(Image)
```
\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n


# Brightness
menyesuaikan kecerahan

```{r}
Image1 <- Image + 0.2
Image2 <- Image - 0.2
par(mfrow= c(1,2))
plot(Image1)
plot(Image2)
```
\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n


# Adjusting Contrast
memanipulasi kontras

```{r}
Image3 <- Image * 0.5
Image4 <- Image * 2
par(mfrow= c(1,2))
plot(Image3)
plot(Image4)
```
\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n



# Gamma Correction
koreksi Gamma
```{r}
Image5 <- Image ^ 2
Image6 <- Image ^ 0.7
par(mfrow= c(1,2))
plot(Image5)
plot(Image6)
```
\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n




#Cropping
```{r}

display(Image[189:1000, 100:600,])

```
\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n




#Transformasi Spasial
```{r}
Imagetr <- translate(rotate(Image, 45), c(50,0))
display(Imagetr)
```
\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n



#Manajemen warna
```{r}
colorMode(Image) <- Grayscale
display(Image)
print(Image)
colorMode(Image) <- Color
display(Image)
```
\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n




#low-pass filter
```{r}
flow <- makeBrush(21, shape= 'disc', step=FALSE)^2
flow <- flow/sum(flow)
Image.flow <- filter2(Image, flow)
display(Image.flow)
```
\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n



#high-pass filter
```{r}
fHigh <- matrix(1, nc=3, nr=3)
fHigh[2,2]<- -8
Image.fHigh <- filter2(Image, fHigh)
display(Image.fHigh)
```
\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n\n





daftar pustaka : https://thinkstudioo.blogspot.com/2018/03/analisis-image-menggunakan-ebimage-di-r_6.html


